Ms. No. PSRM-OA-2019-0126 entitled ``Taking Dyads Seriously''

### 2020-03-02 revisionMemo/rev2.tex
theory for random effects

		We have added an additional interpretation of the random effects on pg. 19 in our discussion of Reiter and Stam. (``Specifically, we can see that countries such as Iraq, Israel, Egypt, and Iran are more likely to be involved in initiating or continuing conflict with other countries than the model would predict. Further, other countries such as Bhutan, Finland, and Turkmenistan are less likely to engage in conflict than the exogenous covariates in the model would suggest. In this case, the finding that countries in the middle east experience more conflict with other countries might lead one to more carefully examine the effects of geography or natural resources on the initiation of conflict.") \textbf{CD}: Likely need to re-write to link to THEORY specifically?

>>>>

		We have added an additional interpretation of the random effects on pg. 19 in our discussion of Reiter and Stam. (``Specifically, we can see that countries such as Iraq, Israel, Egypt, and Iran are more likely to be involved in initiating or continuing conflict with other countries than the model would predict. Further, other countries such as Bhutan, Finland, and Turkmenistan are less likely to engage in conflict than the exogenous covariates in the model would suggest. In this case, the finding that countries in the middle east experience more conflict with other countries might lead one to more carefully examine the effects of geography on conflict initiation or to account for \citet{colgan:2010}'s theory that revolutionary petrostates are more aggressive.") 
